Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-14 ms.tex
more text, another Planck paper in references

\subsection{Smoothing}

@@

\begin{equation}
I_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

\section{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $\tilde{I}_{545}$. To be clear, we are sampling the posterior
given by:

\begin{equation}
P(\tilde{I}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|\tilde{I}_{545}, T_2)P(T_2)
\end{equation}

The likelihood function is given by:

Where the errors on each intensity measurement, $\sigma_{\nu}$ are given by:

In order to obtain reasonable fitting results at high latitude where the
data is noisy, we include a prior on $T_2$

%mention something about the proposal distribution at some point?

@@

>>>>

\subsection{Smoothing}
We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
properly combine these maps, they must have the same PSF. \verb|i100|, with its
$6.1'$ symmetric Gaussian PSF, is the lowest-resolution map we have included. 
To match PSFs, we have therefore smoothed each of the \PLANCK~maps under 
consideration to $6.1'$ resolution by considering each native map to have
a symmetric Gaussian beam and smoothing by the appropriate symmetric Gaussian
such that the resulting map has a FWHM of $6.1'$. The FWHM we assign to the 
native \PLANCK~maps is taken from \cite{planckbeam}, specifically $5.01'$ for
217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.

@@

\begin{equation}
M_{\nu} \propto f_{1}q_{1}(\nu/\nu_{0})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

\section{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
are sampling the posterior given by:

\begin{equation}
P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)
\end{equation}

The likelihood function is given by:
\begin{equation}
\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(M_{\nu_{i}}(\tilde{I}_{545}, T_2)|I_{\nu_{i}}, \sigma_{\nu_i})
\end{equation}

%be more careful about notation re: color corrections

Where the product runs over $\nu_i$ in $\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz. 
For each pixel, the errors on each intensity measurement $\sigma_{\nu_i}$ are 
given by:

\begin{equation}
\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB_{\nu_i} + }
\end{equation}

This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
multiplicative calibration uncertainty for the intensity in each band, and we 
have adopted the values listed in \cite{planckdust} Table 1. We have adopted 
$c_{217 GHz}$ = XX. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:

\begin{equation}
P(T_2) = \mathcal{N}(T_2|\bar{T}_2, \sigma_{\bar{T}_2})
\end{equation}

With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In practice we 
always perform computations using the logarithm of relevant probabilities.
%mention something about the proposal distribution at some point?

@@

%provide maps at multiple different nsides ?
%   -> if so, actually smooth the maps before rebinning, or leave 
%      undersampled?

\subsection{Comparison to Planck Collaboration Dust Map}
